Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add theoretical framework image

>>>>

```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion. Real-world events and linguistic cohesion continually interact and influence one another throughout time."}

# call the image
knitr::include_graphics("./figs/theoretical-framework.png")
